---
title: "compare estimation with model-fitting"
output: html_notebook
author: ruonanjia
---


```{r}
library(tidyverse)
library(ggplot2)
```

Functions
```{r}
# functions
data_summary <- function(data, varname, groupnames){
  # Function to calculate the mean and the standard error
  # for each group
  #+++++++++++++++++++++++++
  # data : a data frame
  # varname : the name of a column containing the variable
  #to be summariezed
  # groupnames : vector of column names to be used as
  # grouping variables
  
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE)/sqrt(length(x[[col]])))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
  return(data_sum)
}

data_meanstd <- function(x) {
  # Function to produce summary statistics (mean and +/- sd)
  m <- mean(x)
  ymin <- m-sd(x)
  ymax <- m+sd(x)
  return(c(y=m,ymin=ymin,ymax=ymax))
}

data_meanse <- function(x) {
  # Function to produce summary statistics (mean and +/- sd)
  m <- mean(x)
  ymin <- m-sd(x)/sqrt(length(x))
  ymax <- m+sd(x)/sqrt(length(x))
  return(c(y=m,ymin=ymin,ymax=ymax))
}
```

Load data
```{r}
path <- "/Users/jiaruonan/Desktop/mdm_covid19/mdm_covid19_data"
setwd(path)

fit_mon <- read.csv("par_08152020.csv", header = TRUE)
exclude_list <- read.csv("exclude_list_mon.csv", header = TRUE)

load("data_all_444sub_rename.Rda")
load("data_all_444sub_rename_header.Rda")
load("data_all_444sub_attitude.Rda")

# combine data
data.all <- merge(data.all, data.attitude, by = "mTurkCode")
data.all$age <- as.numeric(as.character(data.all$age)) + 17 # correct coding

```

Take out the model-fitted parameters, monetary decisions
```{r}
fit_mon$beta_t <- -fit_mon$beta_mon
fit_mon
```

Calculate the model-fitting probability for ambiguity levels
```{r}
ambigs <- c(0.24, 0.5, 0.74,1)

fit_mon$fit_prob_a24 <- 0.5 - ambigs[1]/2*fit_mon$beta_mon
fit_mon$fit_prob_a50 <- 0.5 - ambigs[2]/2*fit_mon$beta_mon
fit_mon$fit_prob_a74 <- 0.5 - ambigs[3]/2*fit_mon$beta_mon
fit_mon$fit_prob_a100 <- 0.5 - ambigs[4]/2*fit_mon$beta_mon

fit_prob <- data.frame(mTurkCode = fit_mon$id,
                       fit_prob_a24 = fit_mon$fit_prob_a24 *100, 
                       fit_prob_a50 = fit_mon$fit_prob_a50*100, 
                       fit_prob_a74 = fit_mon$fit_prob_a74*100,
                       fit_prob_a100 = fit_mon$fit_prob_a100*100)
```

combine table
```{r}
data <- merge(data.all, fit_prob, by="mTurkCode")
# data <- data_all

colnames(data)[c(152:155)] = c("AmbigE_posoutcome_24", "AmbigE_posoutcome_50", "AmbigE_posoutcome_74", "AmbigE_posoutcome_100")
```

reorganize sheet
```{r}

idx = 1
for (amb_level in c("24", "50", "74", "100")) {

  estimate_single = data %>% select(mTurkCode, error.mon, contains(paste("AmbigE_posoutcome_", amb_level, sep = "")), contains(paste("fit_prob_a", amb_level, sep = "")))
  estimate_single$amb_level = as.numeric(amb_level)
  names(estimate_single)[3] = "estimate_amb" 
  names(estimate_single)[4] = "fit_prob_amb"
  
  if (idx == 1) {
    estimate = estimate_single
  } else {
    estimate = rbind(estimate, estimate_single)
  }
  
  idx = idx + 1

  
}

estimate$amb_level = as.factor(estimate$amb_level)
estimate$estimate_amb = as.numeric(as.character(estimate$estimate_amb))

```

Calculate average
```{r}
id <- unique(estimate$mTurkCode)
length(id)
```

Plot estimation by ambiguity level and outcome level
```{r}
# if want to exclude participants
names(estimate)

estimate_plot = estimate[estimate$error.mon < 0.5 & !is.nan(estimate$estimate_amb), ]

tb2plot = data_summary(estimate_plot, varname = "estimate_amb", groupnames = c("amb_level"))

ggplot(data = tb2plot, aes(x = amb_level, y = estimate_amb)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=estimate_amb-sd, ymax=estimate_amb+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Estimation of outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))


```

Plot model-fitted probability by ambiguity level 
```{r}
# if want to exclude participants
names(estimate)

estimate_plot = estimate[estimate$error.mon < 0.5 & !is.na(estimate$estimate_amb) & abs(estimate$fit_prob_amb) < 100, ]

tb2plot = data_summary(estimate_plot, varname = "fit_prob_amb", groupnames = c("amb_level"))

ggplot(data = tb2plot, aes(x = amb_level, y = fit_prob_amb)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=fit_prob_amb-sd, ymax=fit_prob_amb+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Model-fitted outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))


```

reorganize sheet to directly compare subjective and objective estimation
```{r}
subjective = estimate %>% select(mTurkCode, error.mon, estimate_amb, amb_level)
colnames(subjective)[3] = "estimate"
subjective$method <- "subjective"
objective = estimate %>% select(mTurkCode, error.mon, fit_prob_amb, amb_level)
colnames(objective)[3] = "estimate"
objective$method <- "objective"

compare <- rbind(subjective,objective)
compare$method <- as.factor(compare$method)
```

Plot direct comparison between subjective and objective estimation 
```{r}
estimate_plot = compare[compare$error.mon < 0.5 & !is.na(compare$estimate) & abs(compare$estimate) < 100, ]

include_id <- unique(estimate_plot$mTurkCode)

tb2plot = data_summary(estimate_plot, varname = "estimate", groupnames = c("amb_level", "method"))


ggplot(data = tb2plot, aes(x = amb_level, y = estimate, fill=method)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=estimate-sd, ymax=estimate+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Compare outcome probability estimation') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
