---
title: "preprocess"
author: ruonanjia
---
```{r}
library(dplyr)
library(ggplot2)

```


```{r}
rm(list = ls())
```

# Initial cleaning
##read data
```{r}
setwd("E:/Ruonan/Projects in the lab/mdm_covid19/behavior/batch_data/phase2")
# data downloaded from qualtrics, with numeric code 

# young subjects
# data.raw = read.csv("MDM_R&A_COVID-19_Jan2021_Phase2_February+5,+2021_11.02.csv")

# read trial parameters of the DM task
trial.param <- read.csv("trialsinfo_COVID_19.csv", header = TRUE, )
# View(data.raw)
# View(trial.param)
```

```{r}
data.raw
```

##Extract batch data
```{r}

# get rid of excessive header
header <- data.raw[1:2, ]
data.raw <- data.raw[-c(1,2),]
# View(header)
# get rid of preview and incomplete data
data.raw <- data.raw[!data.raw$DistributionChannel == "preview",]
# data.raw <- data.raw[data.raw$Finished == 1, ] # use progress.
data.raw$Progress <- as.numeric(as.character(data.raw$Progress))
data.raw <- data.raw[data.raw$Progress > 75, ]
data.raw <- data.raw[!is.na(as.numeric(as.character(data.raw$mTurkCode))), ]

nrow(data.raw) # check numner of participants


data.batch <- data.raw

nrow(data.batch)

```

##attention check questions, count wrong answers
```{r}
# 
# # or match batch by survey code
# data.batch <- data.raw[is.element(data.raw$mTurkCode, batch$Answer.surveycode),]

# data.batch <- data.raw
# colnames(data.batch)
ac.id <- c("AC_eg", "AC2", "AC3", "AC4", "AC5", "AC6", "AC7", "AC8", "AC9", "AC10", "AC11", "AC12")

is.element(ac.id, colnames(data.batch))

col.no <- match(ac.id, colnames(data.batch))
colnames(data.batch)[col.no]

att.check <- data.batch[, col.no]

correct <- c(2,2,5,5,3,3,2,1,10,6,1,3)

for (i in 1:nrow(att.check)) {
  att.check$wrong[i] = 0 # count how many wrong answers
  for (j in 1:12) {
    if (att.check[i, j] != correct[j]) {
      att.check$wrong[i] <- att.check$wrong[i]+1
    }
  }
}

data.batch$AttCheck <- att.check$wrong

# check the column att.check$wrong, indicating the number of wrong answers
View(att.check)
# those with more than half ATT check Questions wrong
as.character(att.check$mTurkCode[att.check$wrong > 6])

```

## Save data
```{r}
data.all.phase2 <- data.batch
# View(data.all.phase2)
# nrow(data.all.phase2)

# save 
setwd("E:/Ruonan/Projects in the lab/mdm_covid19/behavior/batch_data/phase2")
save(data.all.phase2, file = "data_all_phase2_306sub.Rda")
# save(header, file = "data_all_phase2_306sub_header.Rda")
```
# load data
```{r}
# data.all.phase2 <- data.batch
# View(data.all.phase2)
# nrow(data.all.phase2)

# save 
setwd("E:/Ruonan/Projects in the lab/mdm_covid19/behavior/batch_data/phase2")
load("data_all_phase2_306sub.Rda")

```
Check if the Mturker entered the survey code the same as Qualtrilcs code
Check for multiple responses from same MTurker

# match mTurk worker IDs
Load batch details
```{r}
setwd("E:/Ruonan/Projects in the lab/mdm_covid19/behavior/batch_data/Phase2")
batch1 <- read.csv("Batch_4313780_batch_results.csv")
batch2 <- read.csv("Batch_4316494_batch_results.csv")
batch3 <- read.csv("Batch_4317364_batch_results.csv")
batch4 <- read.csv("Batch_4319627_batch_results.csv")
batch5 <- read.csv("Batch_4321143_batch_results.csv")
batch6 <- read.csv("Batch_4322723_batch_results.csv")
batch7 <- read.csv("Batch_4324048_batch_results.csv")
batch8 <- read.csv("Batch_4325105_batch_results.csv")

batch1_id <- batch1 %>% select(Answer.surveycode, WorkerId)
# correct the survey code. This participant mistakenly put worker ID as the survey code.
batch1_id$Answer.surveycode <- as.integer(as.character(batch1_id$Answer.surveycode))
batch1_id$Answer.surveycode[99] = 77640967

batch2_id <- batch2 %>% select(Answer.surveycode, WorkerId)
batch3_id <- batch3 %>% select(Answer.surveycode, WorkerId)
batch4_id <- batch4 %>% select(Answer.surveycode, WorkerId)
batch5_id <- batch5 %>% select(Answer.surveycode, WorkerId)
batch6_id <- batch6 %>% select(Answer.surveycode, WorkerId)
batch7_id <- batch7 %>% select(Answer.surveycode, WorkerId)
batch8_id <- batch8 %>% select(Answer.surveycode, WorkerId)

batch_id <- rbind(batch2_id, batch3_id, batch4_id, batch5_id, batch6_id, batch7_id, batch8_id)
batch_id$Answer.surveycode <- as.integer(as.character(batch_id$Answer.surveycode))

batch_id <- rbind(batch1_id, batch_id)
# setwd("E:/Ruonan/Projects in the lab/mdm_covid19/batch_data")
# 
# save(batch, file="batch_info.Rda")
```

```{r}
batch_id
nrow(batch_id)
```

if data and batch record match with each other
```{r}
# colnames(batch)
# batch7$Answer.surveycode
data.all.phase2$mTurkCode <- as.integer(as.character(data.all.phase2$mTurkCode))

sum(!is.element(batch_id$Answer.surveycode, data.all.phase2$mTurkCode))
batch_id$Answer.surveycode[!is.element(batch_id$Answer.surveycode, data.all.phase2$mTurkCode)]

sum(!is.element(data.all.phase2$mTurkCode, batch_id$Answer.surveycode))
data.all.phase2$mTurkCode[!is.element(data.all.phase2$mTurkCode, batch_id$Answer.surveycode)]

```

Merge mTurkID
```{r}
colnames(batch_id)[1] <- "mTurkCode"
data.all.phase2<- merge(data.all.phase2, batch_id, by="mTurkCode")
View(data.all.phase2)
```


# take out task data
```{r}
colnames(data.all.phase2)
colnames(data.all.phase2)[c(29:41,43:54,56:79,89:101,103:113,115:139,140:149,151:154,1,278)]

# choice, rating, and ambiguity estimation
data.task.phase2 <- data.all.phase2[,c(29:41,43:54,56:79,89:101,103:113,115:139,140:149,151:154,1,278)]

# View(data.task)
# colnames(data.task)
# change column names for ambiguity estimation
# colnames(data.task)[109:112] <- c("a24.e", "a50.e", "a74.e", "a100.e")
# colnames(data.task)

```


extract choice data
```{r}
# extract choice data and attache trial parameters
# concatenate all subjects

# colnames(trial.param)
# colnames(data.task.phase2)

for (i in 1:nrow(data.task.phase2)) {
  # single subject choice
  sub.choice <- trial.param
  choice <- data.task.phase2[i, 1:98]
  
  id <- as.factor(as.character(data.task.phase2$mTurkCode[i])) # MTurk code
  WorkerID <- as.factor(as.character(data.task.phase2$WorkerId[i])) # worker ID
  
  sub.choice$id <- id
  sub.choice$WorkderID <- WorkerID
  
  sub.choice$choice <- as.numeric(t(choice)) # transpose
  
  # concatenate
  if (i == 1) {
    data.choice <- sub.choice
  } else {
    data.choice <- rbind(data.choice, sub.choice)
  }
}

View(data.choice)

# typeof(data.choice$val)

data.choice.mon.phase2 <- data.choice[data.choice$is_med == 0, ]
data.choice.med.phase2 <- data.choice[data.choice$is_med == 1, ]


data.choice.mon.phase2$val <- as.numeric(as.character(data.choice.mon$val))
data.choice.mon.phase2$prob <- as.factor(data.choice.mon$prob)
data.choice.mon.phase2$ambig <- as.factor(data.choice.mon$ambig)

data.choice.med.phase2$val <- as.factor(data.choice.med$val)
data.choice.med.phase2$prob <- as.factor(data.choice.med$prob)
data.choice.med.phase2$ambig <- as.factor(data.choice.med$ambig)
```

save data
```{r}
setwd("E:/Ruonan/Projects in the lab/mdm_covid19/behavior/batch_data/Phase2")


save(data.choice.mon.phase2, file="data_choice_phase2_mon_306sub.Rda")
save(data.choice.med.phase2, file="data_choice_phase2_med_306sub.Rda")

```

```{r}
data.choice.med.phase2
```

