---
title: "preprocess"
author: ruonanjia
---

```{r}
rm(list = ls())
```


read data
```{r}
setwd("E:/Ruonan/Projects in the lab/mdm_covid19/batch_data")
# data downloaded from qualtrics, with numeric code 

# young subjects
data.raw = read.csv("MDM_R&A_Task_withGraphics_COVID-19_July+12,+2020_16.38.csv")

# older adults
# data.raw = read.csv("MDM_R&A_Task_withGraphics_COVID-19_Older_July+12,+2020_16.39.csv")

# read trial parameters of the DM task
trial.param <- read.csv("trialsinfo_COVID_19.csv", header = TRUE, )
# View(data.raw)
# View(trial.param)
```

Extract batch data
```{r}
# dates for each batch
launch <- data.frame(start=as.Date(c("2020-03-29", "2020-04-06", "2020-04-13", "2020-04-21", "2020-04-27", "2020-05-05")), 
                     end=as.Date(c("2020-03-31", "2020-04-07", "2020-04-14", "2020-04-23", "2020-04-30", "2020-05-06")))

launch_60 <- data.frame(start=as.Date(c("2020-04-17", "2020-04-22","2020-04-27", "2020-04-27", "2020-05-05")), 
                     end=as.Date(c("2020-04-22", "2020-04-26", "2020-04-28", "2020-04-30", "2020-05-06")))

# colnames(data.raw)

# get rid of excessive header
header <- data.raw[1:2, ]
data.raw <- data.raw[-c(1,2),]
# View(header)
# get rid of preview and incomplete data
data.raw <- data.raw[!data.raw$DistributionChannel == "preview",]
# data.raw <- data.raw[data.raw$Finished == 1, ] # use progress.
data.raw$Progress <- as.numeric(as.character(data.raw$Progress))
data.raw <- data.raw[data.raw$Progress > 75, ]
data.raw <- data.raw[!is.na(as.numeric(as.character(data.raw$mTurkCode))), ]

# get rid of lab testing data (by comparing survey startdate)
data.raw <- data.raw[!as.Date(as.character(data.raw$StartDate)) < launch$start[1],] 
data.raw <- data.raw[!(as.Date(as.character(data.raw$StartDate)) > launch$end[1] & as.Date(as.character(data.raw$StartDate)) < launch$start[2]), ]

nrow(data.raw) # check numner of participants
```

attention check questions, count wrong answers
```{r}
# # extract new batch to pay, younger
# data.batch <- data.raw[as.Date(as.character(data.raw$StartDate)) >= launch$start[5] & as.Date(as.character(data.raw$StartDate)) <= launch$end[5], ]
# 
# # older
# data.batch <- data.raw[as.Date(as.character(data.raw$StartDate)) >= launch_60$start[4] & as.Date(as.character(data.raw$StartDate)) <= launch_60$end[4], ]
# 
# # or match batch by survey code
# data.batch <- data.raw[is.element(data.raw$mTurkCode, batch$Answer.surveycode),]

data.batch <- data.raw

nrow(data.batch)
# data.batch <- data.raw
colnames(data.batch)
ac.id <- c("AC_eg", "AC2", "AC3", "AC4", "AC5", "AC6", "AC7", "AC8", "AC9", "AC10", "AC11", "AC12")

# col.no <- c(20,24,42,55,80,84,102,114,150,165,212,266,350)
col.no <- c(20,24,42,55,80,84,102,114,150,165,212,269,353)
colnames(data.batch)[col.no]
att.check <- data.batch[, col.no]

correct <- c(2,2,5,5,3,3,2,1,10,7,1,3)
for (i in 1:nrow(att.check)) {
  att.check$wrong[i] = 0 # count how many wrong answers
  for (j in 1:12) {
    if (att.check[i, j] != correct[j]) {
      att.check$wrong[i] <- att.check$wrong[i]+1
    }
  }
}

data.batch$AttCheck <- att.check$wrong

# check the column att.check$wrong, indicating the number of wrong answers
View(att.check)
# those with more than half ATT check Questions wrong
as.character(att.check$mTurkCode[att.check$wrong > 6])

# data.young <- data.batch
data.old <- data.batch
```

combine young and older data
```{r}
# check if colnames match
match_yo <- is.element(colnames(data.young), colnames(data.old))
match_oy <- is.element(colnames(data.old), colnames(data.young))

which(match_yo == FALSE)
which(match_oy == FALSE)

# a few column names do not match
colnames(data.young)[!match_yo]
colnames(data.old)[!match_yo]

# make column names the same
colnames(data.old) <- colnames(data.young)

# tablenames <- data.frame(young = colnames(data.young), old = colnames(data.old))
# View(tablenames)

# combine data
# data.all <- merge(data.young, data.old, by = colnames(data.young))
data.all <- rbind(data.young, data.old)
View(data.all)
nrow(data.all)

# save 
save(data.all, file = "data_all_444sub_rename.Rda")
save(header, file = "data_all_444sub_rename_header.Rda")
```

Check if the Mturker entered the survey code the same as Qualtrilcs code
Check for multiple responses from same MTurker

Load batch details
```{r}
setwd("E:/Ruonan/Projects in the lab/mdm_covid19/batch_data")
batch1 <- read.csv("Batch_3973824_batch_results.csv")
batch2 <- read.csv("Batch_3983151_batch_results.csv")
batch3 <- read.csv("Batch_3991931_batch_results.csv")
batch4 <- read.csv("Batch_3999031_batch_results.csv")
batch5 <- read.csv("Batch_4003124_batch_results.csv")
batch6 <- read.csv("Batch_4006085_batch_results.csv")
batch7 <- read.csv("Batch_4011935_batch_results.csv")
batch8 <- read.csv("Batch_4012284_batch_results.csv")
batch9 <- read.csv("Batch_4012287_batch_results.csv")
batch10 <- read.csv("Batch_4023483_batch_results.csv")
batch11 <- read.csv("Batch_4023486_batch_results.csv")

batch <- rbind(batch1, batch2, batch3, batch4, batch5, batch6, batch7, batch8, batch9, batch10, batch11)

View(batch)

# setwd("E:/Ruonan/Projects in the lab/mdm_covid19/batch_data")
# 
# save(batch, file="batch_info.Rda")
```

```{r}
# colnames(batch)
# batch7$Answer.surveycode

is.element(batch$Answer.surveycode, data.all$mTurkCode)
is.element(data.all$mTurkCode, batch$Answer.surveycode)
sum(!is.element(data.all$mTurkCode, batch$Answer.surveycode))
# find the survey code with mistake and correct
# one subject mistakenly put MTurk ID as survey code (there is reference in the levylab email)
# 52547965, AFM65NU0UXIGP

data.all$mTurkCode[149]

batch$Answer.surveycode[batch$WorkerId == "AFM65NU0UXIGP"] = "52547965"

```

Check multiple responses from one subject
```{r}
# merge MTurk ID into data sheet
for (i in 1:(nrow(data.all))) {
  if (length(as.character(batch$WorkerId[batch$Answer.surveycode == as.character(data.all$mTurkCode[i])])) != 0) {
    data.all$WorkerId[i] <- as.character(batch$WorkerId[batch$Answer.surveycode == as.character(data.all$mTurkCode[i])])
  } else {
    data.all$WorkerId[i] <- NA
  }
  
}

View(data.all)

# those with missing worker ID, should be 0
sum(is.na(data.all$WorkerId))

nrow(batch)

dupli <- data.all$WorkerId[duplicated(data.all$WorkerId)] 
sort(dupli)
```


MTurkers who answered additional Qs
```{r}
# colnames(data.batch)

header$Q1089.1
# 5 - answered additional Qs
bonus.code <- as.numeric(as.character(data.batch$mTurkCode[data.batch$Q1089.1 == 5]))
# bonus.code
View(bonus.code)
```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

