---
title: "R Notebook"
author: ruonanjia
---


```{r}
rm(list = ls())
```

load library
```{r}
library(ggplot2)
library(zipcode) # install only available through archive
library(maps)
library(ggpubr)
library("PerformanceAnalytics") # for chart correlation
library(usmap) # for plotting data us maps
library(scales) # for muted() function
library(tidyverse)
# library(memisc)
```

# load data
```{r}
# setwd("E:/Ruonan/Projects in the lab/mdm_covid19/batch_data")
setwd("E:/Ruonan/Projects in the lab/mdm_covid19/behavior/mdm_covid19_data")
load("data_all_444sub_rename.Rda")
load("data_all_444sub_rename_header.Rda")
load("data_all_444sub_attitude.Rda")
tracker <- read.csv("testing_by_state.csv", header = TRUE)

# combine data
data.all <- merge(data.all, data.attitude, by = "mTurkCode")
data.all$age <- as.numeric(as.character(data.all$age)) + 17 # correct coding
rm(data.attitude)
```

# Preprocess some data columns, run the following chunks before further analysis:

Separate young and old, compare with 60 yr
```{r}
data.all$is.young <- 1
data.all$is.young[data.all$age >= 60] = 0 
data.all$is.young <- as.factor(data.all$is.young)
```

Clean zipcode
```{r}
# clean zipcode
data.all$zip_postal_code <- as.numeric(as.character(data.all$zip_postal_code))
data(zipcode)
data.all$zipcode<- clean.zipcodes(data.all$zip_postal_code)
```

State based on zip
```{r}
colnames(zipcode)[1] = "zipcode"
data.all <- merge(data.all, zipcode, by="zipcode")
```


```{r}
tracker$state <- as.character(tracker$state)
tracker$week <- as.integer(as.character(tracker$week))
tracker$testing <- as.numeric(tracker$testing)

# no data for AL
typeof(tracker$testing)
```

save into spread sheet
```{r}
# setwd("E:/Ruonan/Projects in the lab/mdm_covid19/behavior/mdm_covid19_data")
# write.csv(header,"data_header_new.csv", row.names = FALSE)
# write.csv(data.all,"data_all_444sub_new.csv", row.names = FALSE)
```
End of preprocessing



# plot trend of testing
```{r}
large_states <- c("FL", "CA", "NY", "OH", "TX")

ggplot(tracker[is.element(tracker$state, large_states),], aes(x = week, y = testing, color = state)) +
  geom_point() +
  scale_x_continuous(breaks=seq(1,6,1)) +
  ggtitle("Number of Testing (3/29 ~ 5/9/2020)")
```

# combine data with case tracker, matching time
```{r}
data.all$testing <- NA
data.all$week <- NA

# if within the week
for (i in 1:nrow(data.all)) {
  if (data.all$state[i] != "AL") {
    data.all$testing[i] <-
      tracker$testing[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
    
    data.all$week[i] <-
      tracker$week[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
  }
}

```

```{r}
data.all$ambig1_react_state <- as.integer(as.character(data.all$ambig1_react_state))

data.all$ambig1_gov_local <- as.integer(as.character(data.all$ambig1_gov_local))
```

#
```{r}
ggplot(data.all[is.element(data.all$state, large_states),], aes(x=testing, y=ambig1_react_state)) +
  geom_point()

cor.test(~ testing + ambig1_react_state,
         data.all[is.element(data.all$state, large_states),]
         )
```

# linear regression
# https://www.statmethods.net/stats/regression.html

```{r}
data.all$week <- ordered(data.all$week, levels = 1:6)
data.all$state <- as.factor(data.all$state)

fit <- lm(ambig1_react_state ~ state + testing + week, 
          data.all[is.element(data.all$state, large_states),])

fit <- lm(ambig1_gov_local ~ state + testing + week, 
          data.all[is.element(data.all$state, large_states),])

summary(fit)

anova(fit)

data.all$ambig1_
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
