---
title: "R Notebook"
author: ruonanjia
---


```{r}
rm(list = ls())
```

load library
```{r}
library(ggplot2)
library(zipcode) # install only available through archive
library(maps)
library(ggpubr)
library("PerformanceAnalytics") # for chart correlation
library(usmap) # for plotting data us maps
library(scales) # for muted() function
library(tidyverse)
# library(memisc)
```

# load data
```{r}
# setwd("E:/Ruonan/Projects in the lab/mdm_covid19/batch_data")
setwd("E:/Ruonan/Projects in the lab/mdm_covid19/behavior/mdm_covid19_data")
load("data_all_444sub_rename.Rda")
load("data_all_444sub_rename_header.Rda")
load("data_all_444sub_attitude.Rda")

# tracker <- read.csv("testing_by_state.csv", header = TRUE)
tracker <- read.csv("all_states_excel_formatted.csv", header=TRUE)

state_name <- read.csv("state_name.csv", header=TRUE)

# combine data
data.all <- merge(data.all, data.attitude, by = "mTurkCode")
data.all$age <- as.numeric(as.character(data.all$age)) + 17 # correct coding
rm(data.attitude)
```

```{r}
# typeof(tracker)

# tracker
# data.all
# state_name
colnames(state_name)[2] <- "State"

tracker <- merge(tracker, state_name, by="State")

tracker
```

# Preprocess some data columns, run the following chunks before further analysis:

Separate young and old, compare with 60 yr
```{r}
data.all$is.young <- 1
data.all$is.young[data.all$age >= 60] = 0 
data.all$is.young <- as.factor(data.all$is.young)
```

Clean zipcode
```{r}
# clean zipcode
data.all$zip_postal_code <- as.numeric(as.character(data.all$zip_postal_code))
data(zipcode)
data.all$zipcode<- clean.zipcodes(data.all$zip_postal_code)
```

State based on zip
```{r}
colnames(zipcode)
colnames(zipcode)[1] = "zipcode"
data.all <- merge(data.all, zipcode, by="zipcode")
```

correct week
```{r}
# in the original data sheet, week 1 refers to the most recent ween

typeof(tracker$Week)
tracker$Week <- 7-tracker$Week
```


```{r}

Week <- c(1,2,3,4,5,6)
date <- c("2020-03-29", "2020-04-05", "2020-04-12", "2020-04-19", "2020-04-26", "2020-05-03")

timing <- data.frame(Week, date)

timing$Week <- as.integer(timing$Week)

tracker <- merge(tracker, timing, by="Week")

# timing
```

Change column names
```{r}
# colnames(tracker)
colnames(tracker)[1] <- "week"
colnames(tracker)[14] <- "state"
colnames(tracker)
```

Change data type
```{r}
tracker$state <- as.character(tracker$state)
tracker$week <- as.integer(as.character(tracker$week))
# tracker$testing <- as.numeric(tracker$testing)

# no data for AL
# typeof(tracker$testing)
```

save into spread sheet
```{r}
# setwd("E:/Ruonan/Projects in the lab/mdm_covid19/behavior/mdm_covid19_data")
# write.csv(header,"data_header_new.csv", row.names = FALSE)
# write.csv(data.all,"data_all_with_tracker.csv", row.names = FALSE)
```
End of preprocessing



# plot trend of testing
```{r}
colnames(tracker)
```


```{r}
large_states <- c("FL", "CA", "NY", "OH", "TX")
```

```{r}
ggplot(tracker[is.element(tracker$state, large_states),], aes(x = week, y = Avg.positive.tests, color = state)) +
  geom_point() +
  scale_x_continuous(breaks=seq(1,6,1)) + 
  ggtitle("Number of Total Positive Testing (3/29 ~ 5/9/2020)")
  
ggplot(tracker[is.element(tracker$state, large_states),], aes(x = week, y = Avg.total.test.results, color = state)) +
  geom_point() +
  scale_x_continuous(breaks=seq(1,6,1)) +
  ggtitle("Number of Total Testing Administered (3/29 ~ 5/9/2020)")

ggplot(tracker[is.element(tracker$state, large_states),], aes(x = week, y = Avg.deaths, color = state)) +
  geom_point() +
  scale_x_continuous(breaks=seq(1,6,1)) +
  ggtitle("Number of Total Death (3/29 ~ 5/9/2020)")

ggplot(tracker[is.element(tracker$state, large_states),], aes(x = week, y = Avg.cumulative.hospitalized, color = state)) +
  geom_point() +
  scale_x_continuous(breaks=seq(1,6,1)) +
  ggtitle("Number of Total Hospitalizations (3/29 ~ 5/9/2020)")

ggplot(tracker[is.element(tracker$state, large_states),], aes(x = week, y = Avg.current.hospitalized, color = state)) +
  geom_point() +
  scale_x_continuous(breaks=seq(1,6,1)) +
  ggtitle("Number of Hospitalizations of This Week (3/29 ~ 5/9/2020)")


ggplot(tracker[is.element(tracker$state, large_states),], aes(x = week, y = Avg.hospitalized.increase, color = state)) +
  geom_point() +
  scale_x_continuous(breaks=seq(1,6,1)) +
  ggtitle("Number of Daily Hospitalization Increase (3/29 ~ 5/9/2020)")
```

```{r}
data_all_sub$Week <- NA


for (i in 1:nrow(data.all)) {
  if (data.all$state[i] != "") {
    data.all$Week[i] <-
      tracker$Week[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
  }
}
```


# combine data with case tracker, matching time
```{r}
# data.all$testing <- NA
data.all$Avg.positive.tests <- NA
data.all$Avg.total.test.results <- NA
data.all$Avg.deaths <- NA
data.all$Avg.cumulative.hospitalized <- NA
data.all$Avg.current.hospitalized <- NA
data.all$Avg.hospitalized.increase <- NA

data.all$week <- NA

# if within the week
for (i in 1:nrow(data.all)) {
  if (data.all$state[i] != "") {
    # data.all$testing[i] <-
    #   tracker$testing[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
    #                     as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
    #                     as.character(data.all$state[i]) == tracker$state]
    
    data.all$Avg.positive.tests[i] <-
      tracker$Avg.positive.tests[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
    
    data.all$Avg.total.test.results[i] <-
      tracker$Avg.total.test.results[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
    
    data.all$Avg.deaths[i] <-
      tracker$Avg.deaths[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
    
    data.all$Avg.cumulative.hospitalized[i] <-
      tracker$Avg.cumulative.hospitalized[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
    
    data.all$Avg.current.hospitalized[i] <-
      tracker$Avg.current.hospitalized[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
    
    data.all$Avg.hospitalized.increase[i] <-
      tracker$Avg.hospitalized.increase[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
    
    data.all$week[i] <-
      tracker$week[as.Date(data.all$StartDate[i])>=as.Date(tracker$date) &
                        as.Date(data.all$StartDate[i])<as.Date(tracker$date)+7 &
                        as.character(data.all$state[i]) == tracker$state]
  }
}

```



```{r}
data.all$ambig1_react_state <- as.integer(as.character(data.all$ambig1_react_state))

data.all$ambig1_gov_local <- as.integer(as.character(data.all$ambig1_gov_local))

data.all$anx_feelingnow <- as.integer(as.character(data.all$anx_feelingnow))
```

```{r}
colnames(tracker)
```

# relationship between tracker and state gov reaction
```{r}
# ggplot(data.all[is.element(data.all$state, large_states),], aes(x=testing, y=ambig1_react_state)) +
#   geom_point()

data2plot <- data.all %>% select(c(state, Avg.hospitalized.increase, ambig1_react_state))
data2plot <- data2plot %>% filter(!is.na(ambig1_react_state))

data2plot$ambig1_react_state <- ordered(data2plot$ambig1_react_state, levels=1:5)


ggplot(data2plot[is.element(data2plot$state, large_states),], 
       aes(x=ambig1_react_state, y=Avg.hospitalized.increase)) + 
  geom_violin() + 
  geom_jitter(shape=16, 
            position=position_jitter(width=0.2, height=0.01),
            size=1,alpha=0.3) +
  scale_x_discrete(labels=c("Completely overreacting", "Somewhat overreacting","Appropriate","Somewhat insufficient", "Completely insufficient")) +
  rotate_x_text(30) +
  xlab("How is state gov reacting") + ylab("number of hospitalization increase")

fit <- lm(Avg.hospitalized.increase ~ ambig1_react_state
  ,data2plot[is.element(data2plot$state, large_states),])

summary(fit)

anova(fit)
```

# relationship between tracker and state gov well-informed
```{r}
data2plot <- data.all %>% select(c(state, testing, ambig1_gov_local))
data2plot <- data2plot %>% filter(!is.na(ambig1_gov_local))

data2plot$ambig1_gov_local <- ordered(data2plot$ambig1_gov_local, levels=1:7)


ggplot(data2plot[is.element(data2plot$state, large_states),], 
       aes(x=ambig1_gov_local, y=testing)) + 
  geom_violin() + 
  geom_jitter(shape=16, 
            position=position_jitter(width=0.2, height=0.01),
            size=1,alpha=0.3) +
  scale_x_discrete(labels=c("Very","Moderately","Somewhat","Uncertain","Somewhat not", "Moderately not","Very not")) +
  rotate_x_text(30) +
  xlab("How well-informed is state go") + ylab("number of testing")

fit <- lm(testing ~ ambig1_gov_local
  ,data2plot[is.element(data2plot$state, large_states),])

summary(fit)

anova(fit)
```

# relationship between tracker and anxiety
```{r}
data2plot <- data.all %>% select(c(state, Avg.deaths, anx_feelingnow))
data2plot <- data2plot %>% filter(!is.na(anx_feelingnow))

data2plot$anx_feelingnow <- ordered(data2plot$anx_feelingnow, levels=1:7)


ggplot(data2plot[is.element(data2plot$state, large_states),], 
       aes(x=anx_feelingnow, y=Avg.deaths)) + 
  geom_violin() + 
  geom_jitter(shape=16, 
            position=position_jitter(width=0.2, height=0.01),
            size=1,alpha=0.3) +
  scale_x_discrete(labels=c("Not at all", "A little", "Somewhat", "A fair amount", "Much", "Very much", "Extremely")) +
  rotate_x_text(30) +
  xlab("How anxious") + ylab("number of deaths")

fit <- lm(Avg.deaths ~ anx_feelingnow
  ,data2plot[is.element(data2plot$state, large_states),])

summary(fit)

anova(fit)
```


```{r}
cor.test(~ testing + ambig1_react_state,
         data.all[is.element(data.all$state, large_states),]
         )

cor.test(~ testing + anx_feelingnow,
         data.all[is.element(data.all$state, large_states),]
         )

cor.test(~ testing + ambig1_gov_local,
         data.all[is.element(data.all$state, large_states),]
         )
```

# linear regression
# https://www.statmethods.net/stats/regression.html

```{r}
data.all$week <- ordered(data.all$week, levels = 1:6)
data.all$state <- as.factor(data.all$state)
data.all$highest_education
data.all$age
data.all$political_typology
data.all$household.earnings
data.all$gender

fit <- lm(ambig1_react_state ~ state + Avg.total.test.results + Avg.positive.tests + Avg.deaths + Avg.hospitalized.increase + week + anx_feelingnow, 
          data.all[is.element(data.all$state, large_states),])

fit <- lm(ambig1_react_state ~ state + testing + week + anx_feelingnow, 
          data.all)

fit <- lm(ambig1_gov_local ~ state + testing + week, 
          data.all[is.element(data.all$state, large_states),])

fit <- lm(anx_feelingnow ~ state + testing + week + ambig1_react_state, 
          data.all[is.element(data.all$state, large_states),])

summary(fit)

anova(fit)
```

# variable selection
```{r}
library(leaps)
```

```{r}
 data.all[is.element(data.all$state, large_states),]$state
temp$state
```


```{r}

temp <- data.all[is.element(data.all$state, large_states),]
temp$state <- as.factor(as.character(temp$state))

leaps<-regsubsets(anx_feelingnow ~ state + testing + week + ambig1_react_state, 
          temp)

# view results
summary(leaps)

plot(leaps,scale="r2")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
